Figures

### 2020-03-02 manuscript/figures.Rmd
note huc4 ordering in caption
note that regions are huc4

```{r maps2, fig.cap = "A) Map of lake locations and B) hydrologic (HUC) regions.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/11_map-1.pdf")
```

@@

```{r re-1, fig.cap = "Regionally varying effect of watershed land-use cover for best-fit lake TP and TN models. Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines). Also shown is a comparison to a zero effect (solid vertical line. Values that do not overlap the population level effect are shaded in red. Coefficient estimates correspond with $\\gamma$ from Equation 1.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/re-1.pdf")
```

>>>>

```{r maps2, fig.cap = "A) Map of lake locations and B) hydrologic (HUC4) regions.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/11_map-1.pdf")
```

@@

```{r re-1, fig.cap = "Regionally varying effect of watershed land-use cover for best-fit lake TP and TN models. Values shown are posterior medians (filled circles) and 95% credible intervals (solid lines) for individual hydrologic units (HUC4s) ordered from top to bottom (west to east). Also shown is a comparison to a zero effect (solid vertical line. Values that do not overlap the population level effect are shaded in red. Coefficient estimates correspond with $\\gamma$ from Equation 1.", warning=FALSE, echo = FALSE}
knitr::include_graphics("../figures/re-1.pdf")
```
